% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Fee Peng}

\basicInfo{
  \email{poofee@hit.edu.cn} \textperiodcentered\
  \phone{(+86) 180-4510-1018} \textperiodcentered\
  }

\basicInfo{
  \addr{Harbin Institute of Technology, No.92, Xidazhi Street, Nangang District, Harbin, China}
}
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Harbin Institute of Technology (HIT)}, Harbin, China}{Sep. 2015 -- Present}
\textit{Phd. student} in Electronics Engineering (EE)
\datedsubsection{\textbf{Harbin Institute of Technology (HIT)}, Harbin, China}{Sep. 2014 -- Jun. 2015}
\textit{Master student} in Electronics Engineering (EE)
\datedsubsection{\textbf{Harbin Institute of Technology (HIT)}, Harbin, China}{Sep. 2010 -- Jun. 2014}
\textit{B.S.} in Electronics Engineering (EE)

\section{\faCogs\ Publications}
\begin{itemize}[parsep=0.5ex]
  \item Wenying Yang, \textbf{Fei Peng}, Venkata Dinavahi. Nonlinear Axisymmetric Magnetostatic Analysis for Electromagnetic Device using TLM-based Finite Element Method.  IEEE Trans. on Magnetics. 2016. (submitted)
  \item Bing Li, Wenying Yang, \textbf{Fei Peng}, Guofu Zhai. Influence of Electromagnetic Pulse on Electromagnetic Relay by using Equivalent Circuit Model. The 26th International Conference on Electrical Contacts. 2012:180-185. (EI)
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{National Scholarship for Encouragement (2 times)}{2012, 2013}
\datedline{HIT Technology Innovation Second Prize}{2011}
\datedline{HIT People Scholarship (5 times)}{2010-2014}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{FLAG Inc.} California, America}{2012 -- Present}
\role{Summer Intern}{Manager: xxx}
Brief introduction: xxx.
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{xxx Projects}}{Jan. 2015 -- Present}
\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
Brief introduction: xxx
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
\role{\LaTeX, Maintainer}{Individual Projects}
An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == Python > C++ > Java
  \item Platform: Linux
  \item Development: Web, xxx
\end{itemize}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://your.blog.me
  \item GitHub: https://github.com/username
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
